Research Notes

### 2018-08-01 writeups/notes.tex
update ns as well

The method of characteristics then requires we seek linear combinations of the
two equations such that all equations are in characteristic form. The Whitham
prescription says that if the original system is of form $A_{ij}q_{j, t} +
B_{ij}q_{j, x} = 0$, then the characteristic curves $X(T)$ satisfy $A_{ij}X +
B_{ij}T = 0$. Here, this yields
\begin{equation}
    X(T) = \p*{\pd{\omega_0}{x} \pm A\sqrt{\omega_2 \ptd{\omega_0}{k}}}T.
\end{equation}

Comparing to the NLSE dispersion relation \autoref{eq:nlse_disp}, we identify
that $\sqrt{-q \ptd{\omega_0}{k}}A$ is the correction to the group velocity.
Thus, if $q\ptd{\omega_0}{k} > 0$, we obtain a \emph{complex} group velocity,
which is identified with \emph{modulational instability}. Naively, this might
imply a steepening $k = c_{g, 0}t - i\sqrt{q\omega_0''}t$ with timescale
$\Gamma \sim A\p*{q\omega_0''}^{-1/2}$.

>>>>

The method of characteristics then requires we seek linear combinations of the
two equations such that all equations are in characteristic form. The Whitham
prescription says that if the original system is of form $A_{ij}q_{j, t} +
B_{ij}q_{j, x} = 0$, then the characteristic curves $X(T)$ satisfy $A_{ij}X +
B_{ij}T = 0$. Here, this yields
\begin{equation}
    X(T) = \p*{\pd{\omega_0}{k} \pm A\sqrt{\omega_2 \ptd{\omega_0}{k}}}T.
\end{equation}

Comparing to the NLSE dispersion relation \autoref{eq:nlse_disp}, we identify
that $\sqrt{-\nu \ptd{\omega_0}{k}}A$ is the correction to the group velocity.
Thus, if $\nu\ptd{\omega_0}{k} > 0$, we obtain a \emph{complex} group velocity,
which is identified with \emph{modulational instability}. Naively, this might
imply a steepening $k = c_{g, 0}t - i\sqrt{\nu\omega_0''}At$ with timescale
$\Gamma \sim \p*{A^2\nu\omega_0''}^{-1/2}$.
